\documentclass[11pt,letterpaper]{article}

\include{pkgs}
\input{cmds}

% \usepackage{kotex}

\begin{document}

% Name, phone, email, address
{\bf\huge Insu Yun} \vspace{1em}\\
\noindent\begin{tabular}[t]{@{}l}
  Associate Professor (Untenured) \\
  School of Electrical Engineering, \\
  Korea Advanced Institute of Science and Technology (KAIST)
\end{tabular}
\hfill
\begin{tabular}[t]{r@{}}
\\
Email: \email{insuyun@kaist.ac.kr} \\
Web: \href{https://insuyun.github.io}{https://insuyun.github.io} \\
\end{tabular}

%
% Research Interests
%

\sectiontitle{Research Interests}
System security, software security, binary analysis, fuzzing, and applied cryptography.

%
% Education
%

\sectiontitle{Education}
\begin{topic}{Georgia Institute of Technology}{Aug. 2015 -- Dec. 2020}
	\item Ph.D. in Computer Science
	\item Advisor: Dr. Taesoo Kim
\end{topic}

\begin{topic}{Korea Advanced Institute of Science and Technology (KAIST)}{Sep. 2008 -- Feb. 2015}
\item B.S. in Computer Science \& Mathematics
\end{topic}

%
% Work Experience
%

\sectiontitle{Work Experience}
\begin{topic}[Daejeon, South Korea]{KAIST}{Feb. 2021 --}
\item Assistant Professor
\end{topic}
\begin{topic}[Research Intern, Seattle, WA]{Microsoft Research}{May. 2017 -- Aug. 2017}
\item Contributed to REPT, a system that utilizes Intel Processor Trace to diagnose production failures
  \item Mentor:  Weidong Cui
\end{topic}
\subsectiontitle[Research Assistant, Atlanta, GA]{Georgia Tech}{Aug. 2015 -- Dec. 2020} \\
\begin{topic}[Software Developer, Seoul, Korea]{Korean Cyber Command}{Apr. 2012 -- Jan. 2014}
  \item Served for the mandatory military service
\end{topic}


%
% Publications
%

\sectiontitle{Publications}

\textbf{International Conferences \forkaist{(\toptier{Top-tier} and others)}{}}
\begin{etaremune}
  {{ INTL_CONF }}
\end{etaremune}

\textbf{International Journal}
\begin{etaremune}
  {{ INTL_JOURNAL }}
\end{etaremune}

\begin{comment}
\textbf{Domestic Conferences}
\begin{etaremune}
  {{ DOM_CONF }}
\end{etaremune}
\end{comment}

\textbf{Other Refereed Materials}
\begin{etaremune}
  {{ NOPUB }}
\end{etaremune}

\textbf{Thesis}
\begin{etaremune}
\item \textbf{Concolic Execution Tailored for Hybrid Fuzzing}  \\
{\footnotesize
  \textbf{Insu Yun} \\
  Ph.D. thesis, Georgia Institute of Technology \\
Atlanta, GA, December 2020
}
\end{etaremune}

\sectiontitle{Professional Activities}
\begin{topic}{Technical Program Committee (International)}{}
  \item{Program Committee, \emph{IEEE Symposium on Security and Privacy (Oakland)}, 2024--2026}
  \item{Program Committee, \emph{Network and Distributed System Security Symposium (NDSS)}, 2024--2026}
  \item{Program Committee, \emph{The International Conference on Cryptology and Network Security (CANS)}, 2025}
  \item{Program Committee, \emph{ACM Conference on Security and Privacy in Wireless and Mobile Networks (WiSec)}, 2022--2023}
\end{topic}

\begin{topic}{Journal Editor (International)}{}
  \item{Associate Editor, \emph{ACM Transaction on Storage (ToS)}, 2024--2026} % 24.07.15 -
\end{topic}

\begin{topic}{Others (International)}{}
  \item{Organization Committee, \emph{ACM Conference on Security and Privacy in Wireless and Mobile Networks (WiSec)}, 2024} % 23.09.27 - 24.05.30
  \item{Artifact Evaluation Committee, \emph{ACM Conference on Computer and Communications Security (CCS)}, 2023} % 23.10.21 - 23.11.30
  \item{Artifact Evaluation Committee, \emph{USENIX Security Symposium (Security)}, 2023} % 22.09.23 - 23.08.11
  \item{Organization Committee, \emph{ACM Conference on Computer and Communications Security (CCS)}, 2021} % 21.01.15 - 21.11.19
\end{topic}

\begin{topic}{Technical Program Committee (Domestic)}{}
  \item{Program Committee, \emph{Conference on Information Security and Cryptography Summer (CISC-S)}, 2026}
  \item{Program Committee, \emph{Conference on Information Security and Cryptography Winter (CISC-W)}, 2025}
  \item{Program Committee, \emph{Conference on Information Security and Cryptography Summer (CISC-S)}, 2021}
\end{topic}

\begin{topic}{Others (Domestic)}{}
  \item{Policy Advisory Committee, \emph{Ministry of National Defense}, 2026}
  \item{Security Special Committee, \emph{National Artificial Intelligence Strategy Committee}, 2026}
  \item{Security Task Force, \emph{National Artificial Intelligence Strategy Committee}, 2025} % 25.10.01 -
  \item{Advisory Boards, \emph{AI Cyber Defense Contest (ACDC)}, 2025}
  \item{Advisory Boards, \emph{HackTheon Sejong}, 2024--2025} % 23.07.31 - 24.06.21
  \item{Organization Committee, \emph{Conference on Information Security and Cryptography Summer (CISC-S)}, 2021} % 21.03.12 - 21.06.24
\end{topic}


% \begin{topic}{International Conference (External Reviewer)}{}
%   \item{External Reviewer, \emph{Network and Distributed System Security Symposium (NDSS)}, 2023}
%   \item{External Reviewer, \emph{Network and Distributed System Security Symposium (NDSS)}, 2022}
%   \item{External Reviewer, \emph{Network and Distributed System Security Symposium (NDSS)}, 2021}
%   \item{External Reviewer, \emph{Network and Distributed System Security Symposium (NDSS)}, 2020}
%   \item{External Reviewer, \emph{ACM Conference on Computer and Communications Security (CCS)}, 2019}
%   \item{External Reviewer, \emph{USENIX Symposium on Operating Systems Design and Implementation (OSDI)}, 2018}
%   \item{External Reviewer, \emph{USENIX Security Symposium (Security)}, 2018}
%   \item{External Reviewer, \emph{USENIX Annual Technical Conference (ATC)}, 2018}
%   \item{External Reviewer, \emph{Network and Distributed System Security Symposium (NDSS)}, 2018}
%   \item{External Reviewer, \emph{ACM Conference on Computer and Communications Security (CCS)}, 2017}
%   \item{External Reviewer, \emph{ACM Conference on Computer and Communications Security (CCS)}, 2015}
%   \item{External Reviewer, \emph{IEEE Symposium on Security and Privacy (Oakland)}, 2015}
%   \item{External Reviewer, \emph{ACM Conference on Computer and Communications Security (CCS)}, 2014}
%   \item{External Reviewer, \emph{ACM Conference on Security and Privacy in Wireless and Mobile Networks (WiSec)}, 2014}
%   \item{External Reviewer, \emph{IEEE Symposium on Security and Privacy (Oakland)}, 2014}
%   \item{External Reviewer, \emph{Network and Distributed System Security Symposium (NDSS)}, 2014}
%   \item{External Reviewer, \emph{IEEE Symposium on Security and Privacy (Oakland)}, 2013}
% \end{topic}

% Teaching Experience
\sectiontitle{Teaching Experience}
% \textbf{Instructor}
\begin{topic}{}{}
  \entry{Advanced Programming Techniques for Electrical Engineering (EE309 at KAIST)}{Fall 2025}
  \begin{subtopic}
    \item Evaluation --  Average: 4.29 / 5
  \end{subtopic}
  \entry{Software Hacking  Theory and Practice (EE517 at KAIST)}{Spring 2025}
  \begin{subtopic}
    \item Evaluation --  Average: 4.67 / 5
  \end{subtopic}
  \entry{Advanced Programming Techniques for Electrical Engineering (EE309 at KAIST)}{Fall 2024}
  \begin{subtopic}
    \item Evaluation --  Average: 4.54 / 5
  \end{subtopic}
  \entry{Information Security Laboratory (IS521 at KAIST)}{Fall 2024}
  \begin{subtopic}
    \item Evaluation --  Average: 4.64 / 5
  \end{subtopic}
  \entry{Software Hacking  Theory and Practice (EE517 at KAIST)}{Spring 2024}
  \begin{subtopic}
    \item Evaluation --  Average: 4.92 / 5
  \end{subtopic}
  \entry{Advanced Programming Techniques for Electrical Engineering (EE309 at KAIST)}{Fall 2023}
  \begin{subtopic}
    \item Evaluation --  Average: 4.57 / 5
  \end{subtopic}
  \entry{Software Hacking  Theory and Practice (EE517 at KAIST)}{Spring 2023}
  \begin{subtopic}
    \item Evaluation --  Average: 4.54 / 5
  \end{subtopic}
%  \entry{My Life and Career in EE I (EE485-C at KAIST)}{Spring 2023}
%  \begin{subtopic}
%    \item Evaluation --  Average: 4.80 / 5
%  \end{subtopic}
  \entry{Programming Structures for Electronical Engineering (EE209 at KAIST)}{Fall 2022}
  \begin{subtopic}
    \item Evaluation --  Average: 4.65 / 5
  \end{subtopic}
  \entry{Software development environment and tools practice (EE485-A at KAIST)}{Fall 2022}
  \begin{subtopic}
    \item Evaluation --  Average: 4.43 / 5
  \end{subtopic}
%  \entry{My Life and Career in EE II (EE485-C at KAIST)}{Fall 2022}
%  \begin{subtopic}
%    \item Evaluation --  Average: 4.70 / 5
%  \end{subtopic}
  \entry{Software Security (EE595-B at KAIST)}{Spring 2022}
  \begin{subtopic}
    \item Evaluation --  Average: 5 / 5
  \end{subtopic}
%  \entry{My Life and Career in EE I (EE485-C at KAIST)}{Spring 2022}
%  \begin{subtopic}
%    \item Evaluation --  Average: 4.65 / 5
%  \end{subtopic}
  \entry{Programming Structures for Electronical Engineering (EE209 at KAIST)}{Fall 2021}
  \begin{subtopic}
    \item Evaluation --  Average: 4.34 / 5
  \end{subtopic}
  \entry{Software development environment and tools practice (EE485-A at KAIST)}{Fall 2021}
  \begin{subtopic}
    \item Evaluation --  Average: 4.34 / 5
  \end{subtopic}
%  \entry{My Life and Career in EE II (EE485-C at KAIST)}{Fall 2021}
%  \begin{subtopic}
%    \item Evaluation --  Average: 4.57 / 5
%  \end{subtopic}
  \entry{Software Security (EE595-B at KAIST)}{Spring 2021}
  \begin{subtopic}
    \item Evaluation --  Average: 4.9 / 5
  \end{subtopic}
\end{topic}

% \textbf{Teaching Assistant}
% \begin{topic}{}{}
%   \entry{Teaching Assistant, Information Security Lab -- Official (CS8803 at Georgia Tech)}{Fall 2018}
%   \begin{subtopic}
%     \item Evaluation --  Overall Effectiveness: 5 / 5
%   \end{subtopic}
%   \entry{Teaching Assistant, Information Security Lab -- Unofficial (CS8803 at Georgia Tech)}{Fall 2017}
%   \entry{Teaching Assistant, Information Security Lab -- Official (CS6265 at Georgia Tech)}{Fall 2016}
%   \begin{subtopic}
%     \item Evaluation --  Overall Effectiveness: 4.9 / 5
%   \end{subtopic}
%   \entry{Teaching Assistant, Information Security Lab -- Unofficial (CS6265 at Georgia Tech)}{Fall 2015}
%   \entry{Head Instructor, Information Security class for freshmen (KAIST)}{Mar. 2009 -- Aug. 2011}
% \end{topic}

% Honors & Awards
\sectiontitle{Honors \& Awards}
\begin{topic}{Academic awards}{}
  \entry{Song-Am Future Researcher Award}{KAIST}{Feb. 2025} % 2025.02.12
  \entry{Technology Innovation Awards, KAIST College of Engineering}{Dec. 2024} % 2024.12.17
  \entry{Best Teaching Award, KAIST Electrical Engineering}{Oct. 2024} % 2024.10.14
  \entry{Prize for Excellence in Teaching, KAIST}{Feb. 2024}
  \entry{Frontiers of Science Award, The First International Congress of Basic Science (ICBS)}{July. 2023}
  \entry{Best Teaching Award, KAIST Electrical Engineering}{Sep. 2021}
  \entry{Jay Lepreau Best Paper Award, USENIX OSDI 2018}{Aug. 2018}
  \entry{Distinguished Paper Award, USENIX Security 2018}{Aug. 2018}
\end{topic}

\begin{topic}{\forkaist{Hacking competitions}{Capture the flag}}{}
  \entry{DEFCON 26 CTF, 1st place (Team DEFKOR00T)}{Aug. 2018}
  \entry{DEFCON 24 CTF, 3rd place (Team DEFKOR)}{Aug. 2016}
  \entry{DEFCON 23 CTF, 1st place (Team DEFKOR)}{Aug. 2015}
  \entry{Whitehat contest 2014, 1st place (Team SysSec)}{Nov. 2014}
  \entry{DEFCON 22 CTF, 10th place (Team GoN)}{Aug. 2014}
  \entry{SECCON CTF 2014, 1st place (TOEFL Beginner)}{Feb. 2014}
  \entry{Codegate CTF 2012, 3rd place (Team GoN)}{Apr. 2012}
  \entry{Secuinside CTF, 3rd place (Team GoN)}{Oct. 2011}
  \entry{ISEC CTF, 1st place (Team GoN)}{Sep. 2011}
  \entry{DEFCON 18 CTF, 3rd place (Team GoN)}{Aug. 2010}
  \entry{Codegate CTF 2010, 5th place (Team GoN)}{Apr. 2010}
  \entry{KISA HDCON, Gold Medal, 2nd place (Team GoN)}{May 2009}
  \entry{Codegate CTF 2009, 4th place (Team GoN)}{Apr. 2009}
\end{topic}
%
\begin{topic}{Scholarships}{}
  \entry{National Research Foundation of Korea Scholarship for Undergraduate}{Mar. 2008 -- Dec. 2013}
\end{topic}

\begin{topic}{Others}{}
  \entry{DARPA AIxCC, 1st place (Team Atlanta), \$4M award}{Aug. 2025}
  \entry{Cyber Security Challenge, 2nd place (Team HackingLab), \$400K research grant}{2023}
  \entry{DARPA Cyber Grand Challenge, Finalist (Team Disekt)}{Aug. 2016}
  \entry{KISA Bug Bounty Program's Hall of Fame}{2013}
\end{topic}


\sectiontitle{Vulnerability Discovery Reward (aka Bug bounty)}
To summarize, \$244.6K (by my students) and \$92.8K (by myself) bug bounties are awarded so far.

% TODO: Add type confusion
\begin{topic}{By my students}{}
  \entry{Pwn2Own - Microsoft Edge and Google Chrome (\$145K), ZDI, by SeunHyun Lee}{Mar. 2024}
  \entry{v8CTF - CVE-2023-6702 (\$10K), Google, by Haein Lee}{Jan. 2024}
  \entry{kernelCTF - CVE-2023-3390 (\$67.8K), Google, by Dongok Kim and SeunHyun Lee}{Oct. 2023}
  \entry{Type confusion in V8 (\$7K), Google, by Haein Lee}{Mar. 2023}
  \entry{NAS authentication bypass in Exynos (\$14.8K), Samsung Electronics, by Eunsoo Kim and CheolJun Park}{Feb. 2022}
\end{topic}
%

\begin{topic}{By myself}{}
  \entry{PSV-2021-0304: afpd auth bypass (\$300), NETGEAR}{Mar. 2021}
  \entry{Pwn2Own Apple Safari with a kernel privilege escalation (\$70K), ZDI,
    with Yonghwi Jin and Jungwon Lim}{Mar. 2020}
  \entry{Apple Safari sandbox escape (\$20K), Apple}{Dec. 2019}
  \entry{Three integer overflow vulnerabilities in PHP (\$1.5K), the Internet Bug Bounty}{Jun. 2016}
  \entry{An Integer Overflow in Python zipimport (\$1K), the Internet Bug Bounty}{Apr. 2016}
\end{topic}


\begin{comment}
\sectiontitle{Reported Security Vulnerabilities}
  {{ CVE }}
\end{comment}

\sectiontitle{Patents}

\textbf{International}
\begin{etaremune}
  \patentpending{Dynamic testing method and system for detecting memory corruptions in lower layers of cellular baseband of mobile communication devices}{Yongdae Kim, Hoang Dinh Tuan, Insu Yun, Taekkyung Oh, Beomseok Oh, Mincheol Son, CheolJun Park}{2026.01.07}{19442669}{US}
  \patent{Security analysis system and method based on negative testing for protocol implementation of LTE device}{Yongdae Kim, CheolJun Park, Sangwook Bae, Beomseok Oh, Jiho Lee, Mincheol Son, Insu Yun}{12511402}{2025.12.30}{US}
  \patent{Reverse debugging of software failures}{Weidong Cui, Xinyang Ge, Baris Kasikci, Cengiz Can, Ben Niu, Ruoyu Wang, Insu Yun}{10565511}{2020.02.18}{US}
\end{etaremune}

\textbf{Domestic}
\begin{etaremune}
  \patentpending{Method and apparatus for detecting memory vulnerabilities based on network-side state control in wireless communication systems}{Yongdae Kim, Beomseok Oh, Insu Yun, Mincheol Son, Hoang Dinh Tuan, Soohwan Jeong, CheolJun Park}{2025.12.03}{10-2025-0189113}{Korea}
  \patentpending{Method and apparatus for fuzzing-based vulnerability detection}{Insu Yun, Eunkyu Lee, Junyeong Park}{2025.11.11}{10-2025-0169729}{Korea}
  \patentpending{Dynamic testing method and system for detecting memory vulnerabilities in lower layers of cellular baseband of mobile communication devices}{Yongdae Kim, Taekkyung Oh, Beomseok Oh, Mincheol Son, CheolJun Park, Hoang Dinh Tuan, Insu Yun}{2025.05.07}{10-2025-0059118}{Korea}
  \patentpending{Heuristic-based binary lifting and verification system}{Sukyoung Ryu, Jihee Park, Insu Yun}{2025.03.31}{10-2025-0041131}{Korea}
  \patent{Method and apparatus for decompilation-specialized static binary translation}{Insu Yun, Woosun Song, Seunggi Min}{10-2834292-0000}{2025.07.10}{Korea}
  \patent{Security analysis system and method based on negative testing for protocol implementation of LTE device}{Yongdae Kim, CheolJun Park, Sangwook Bae, Beomseok Oh, Jiho Lee, Mincheol Son, Insu Yun}{10-2514797-0000}{2023.03.23}{Korea}
  \patent{Method and system for automatically analyzing bugs in cellular baseband software using comparative analysis based on cellular specifications}{Yongdae Kim, Eunsoo Kim, Dongkwan Kim, CheolJun Park, Insu Yun}{10-2546946-0000}{2023.06.20}{Korea}
  \patent{Methods and systems for key management service provision}{Dongsoo Han, JuHyeng Han, Insu Yun}{10-2803138-0000}{2025.04.28}{Korea}
  \patentpending{Security analysis system based on negative testing for protocol implementation of LTE device}{Yongdae Kim, CheolJun Park, Sangwook Bae, Beomseok Oh, Jiho Lee, Mincheol Son, Insu Yun}{2021.10.07}{10-2021-0133149}{Korea}
\end{etaremune}

% Invited Talks
\sectiontitle{Invited Talks}

\textbf{International}
\begin{topic}{}{}
  \talk{Atlantis: an Autonomous LLM-Powered Bug Finding and Fixing System}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Presented at KAIST-NYU Workshop}{Nov. 2025} % 2025.11.11
  \end{itemize}

  \talk{How to build Skynet --- a system that hacks systems}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{\textbf{Keynote} speech at TyphoonCon, Seoul, Korea}{Jun. 2023} % 2023.06.15
  \end{itemize}

  \talk{HardsHeap: A Universal and Extensible Framework for Evaluating Secure Allocators}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Presented at ACM CCS 2021, Online}{Nov. 2021}
  \end{itemize}

  \talk{Automatic Techniques to Systematically Discover New Heap Exploitation Primitives}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Presented at USENIX Security 2020, Online}{Aug. 2020}
  \end{itemize}

  \talk{QSYM: A Practical Concolic Execution Engine Tailored for Hybrid Fuzzing}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Presented at USENIX Security 2018, Baltimore, MD}{Aug. 2018}
  \end{itemize}

  \talk{APISan: Sanitizing API Usages through Semantic Cross-checking}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Presented at USENIX Security 2016, Austin, TX}{Aug. 2016}
  \end{itemize}
\end{topic}


\textbf{Domestic}
\begin{topic}{}{}
  \talk{The Singularity is Here: When AI Meets Cyber Security}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Seminar at Tech-Share by Samsung Electronics, Hyundai Motor, and Naver, Seoul, Korea}{Feb. 2026} % 2026.02.09
  \end{itemize}

  \talk{The Dark and Bright Sides of AI in Cybersecurity}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Seminar at Samsung Electronics DS, Seoul, Korea}{Jan. 2026} % 2026.01.08
    \entry{Seminar at AI Security Technology Seminar, Seoul, Korea}{Dec. 2025} % 2025.12.05
    \entry{Seminar at KAIST AI Graduate School Colloquium}{Oct. 2025} % 2025.10.28
    \entry{Seminar at KISA, Seoul, Korea}{Oct. 2025} % 2025.10.29
    \entry{Seminar at KISIA, Seoul, Korea}{Oct. 2025} % 2025.10.29
    \entry{Seminar at KAIST-Cyber Security Policy Program}{Sep. 2025} % 2025.09.12
    \entry{Seminar at Samsung SDS, Seoul, Korea}{Sep. 2025} % 2025.09.22
    \entry{Seminar at National Intelligence Service, Seoul, Korea}{Sep. 2025} % 2025.09.29
  \end{itemize}

  \talk{AI that Changed the Cybersecurity Talent and Education}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{\textbf{Keynote} at Cybersecurity Talent Development Symposium, Seoul, Korea}{Dec. 2025} % 2025.12.19
    \entry{Seminar at Cyber Security Policy Forum, Seoul, Korea}{Dec. 2025} % 2025.12.04
  \end{itemize}

  \talk{The Future of Security Transformed by AI}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Seminar at ACDC (AI Cyber Defense Contest), Seoul, Korea}{Dec. 2025} % 2025.12.01
  \end{itemize}

  \talk{AI that Changed the Battlefield}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{\textbf{Keynote} at WhiteHat 2025, Seoul, Korea}{Nov. 2025} % 2025.11.21
  \end{itemize}

  \talk{Atlantis: an Autonomous LLM-Powered Bug Finding and Fixing System}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Seminar at Cyber Security Society, Seoul, Korea}{Nov. 2025} % 2025.11.07
    \entry{Seminar at Cyber Summit Korea 2025, Seoul, Korea}{Sep. 2025} % 2025.09.10
    \entry{Seminar at Tech-Share by Samsung Electronics, Hyundai Motor, and Naver, Seoul, Korea}{Aug. 2025} % 2025.09.19
    \entry{Seminar at ENKI WhiteHat, Seoul, Korea}{Sep. 2025} % 2025.09.26
    \entry{Seminar at LIGNex1, Seoul, Korea}{Sep. 2025} % 2025.09.25
    \entry{Seminar at KCSCON, Seoul, Korea}{Sep. 2025} % 2025.09.30
  \end{itemize}

  \talk{AIxCC: The Future of Cybersecurity with LLMs}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Seminar at ETRI, Daejeon, Korea}{Nov. 2024} % 2024. 11.18
    \entry{Seminar at Moon Sool Graduate School of Future Strategy, Daejeon, Korea}{Nov. 2024} % 2024. 11.12
    \entry{Seminar at Future Security Tech Forum, Jeju, Korea}{Nov. 2024} % 2024. 11.15
    \entry{Seminar at National Security Research Institute (NSRI), Daejeon, Korea}{Sep. 2024} % 2024. 09.06
  \end{itemize}

  \talk{2024 Security Strategy: Polarization}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Seminar at Defense Counterintelligence Command, Gwacheon, Korea}{May. 2024} % 2024.05.09
  \end{itemize}

  \talk{Building Automated Hacking Systems}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Seminar at POSTECH, Pohang, Korea}{Nov. 2023} % 2023.11.10
  \end{itemize}

  \talk{Trends in Security Vulnerabilities of Low Earth Orbit Satellites}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Presented at ETRI, Daejeon, Korea}{Aug. 2023} % 2023.08.31
  \end{itemize}

  \talk{Academic Research from Offensive Research}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Presented at Samsung, Seoul, Korea}{Aug. 2023} % 2023.08.22
  \end{itemize}

  \talk{Human-friendly binary analysis}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Presented at ETRI, Daejeon, Korea}{Nov. 2023} % 2023.11.14
    \entry{Presented at Korea Computer Congress (KCC), Seoul, Korea}{Jun. 2023} % 2023.06.19
  \end{itemize}

  \talk{Exploit in the wild}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Presented at ETRI, Daejeon}{Jun. 2023} % 2023.06.14
  \end{itemize}

  \talk{Hacking 101}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Presented at WISC, Seoul}{Sep. 2022} % 2022.9.6
  \end{itemize}

  \talk{Attack and Defenses for Heap Vulnerabilities in 2022}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Seminar at ETRI, Daejeon}{Apr. 2022} % 2022.4.12
  \end{itemize}

  \talk{Comparative Analysis of Baseband Software and Cellular Specifications for Finding Vulnerabilities}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Seminar at UNIST, Ulsan}{May. 2023}  % 2023.5.17
    \entry{Seminar at Security@KAIST, Online}{Jun. 2022} % 2022.06.22
    \entry{Seminar at Cyber Operations Command, Seoul}{Jun. 2022} % 2022.06.10
  \end{itemize}

  \talk{Scalable and Automatic Vulnerability Discovery Beyond Random Testing}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    Seminar at Seoul National University, Seoul, Korea, Mar. 2019 % 2019.03.11
  \end{itemize}

  \talk{Memory Allocator Security}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Presented at Best of Best (BoB), Seoul}{Feb. 2023}  % 2023.02.09
    \entry{Presented at Computer System Society Conference (CSC), Pyeongchang}{Feb. 2023}  % 2023.02.07
    \entry{Seminar at UNIST, Online}{May. 2022}  % 2022.5.18
    \entry{Seminar at Yonsei university, Online}{Apr. 2022}  % 2022.4.28
    \entry{Seminar at Sungkyunkwan university, Online}{Apr. 2022}  % 2022.4.27
    \entry{Seminar at ETRI, Daejeon}{Jan. 2022}  % 2022.1.25
    \entry{Seminar at National Security Research Institute (NSRI), Daejeon}{Dec. 2021}  % 2021.12.09
    \entry{Seminar at Securty@KAIST, Online}{Nov. 2021}  % 2021.11.24
    \entry{Seminar at KAIST GSIS, Online}{Nov. 2021} % 2021.11.23
  \end{itemize}

  \talk{Browser Security: Hacking \& Research}{}
  \begin{itemize}[label=--]
    \setlength\itemsep{-0.5em}
    \vspace{-5px}
    \entry{Presented at Open Theori Research Seminar \#6, Online}{Dec. 2021} % 2021.12.23
    \entry{Seminar at Hanyang University, Online}{Nov. 2021} % 2021.11.17
    \entry{Presented at KR Becks Meetup \#1 by LINE, Online}{Aug. 2021} % 2021.08.13
    \entry{Seminar at Security@KAIST, Online}{Jun. 2021} % 2021.06.23
\end{itemize}


\end{topic}
\sectiontitle{Grants}

To summarize, 2.4B KRW is awarded, and my portion is 1.96B KRW.
\vspace{0.5em}

\begin{etaremune}
  \grant{Intelligent multi-agent system for variant vulnerability detection in large-scale software}{NRF}{142M}{PI}{26.03 -- 27.02}
  \grant{Design and implementation of novel fuzzing system for USB driver security}{Samsung Electronics}{82.5M}{PI}{25.08 -- 26.05}
  \grant{SAT-HACK: Satellite cyber kill chain verification research}{LIGNex1}{275M}{PI}{25.07 -- 27.02}
  \grant{Software safety research based on automated vulnerability pattern generation}{NSRI}{60M}{PI}{25.04 -- 25.10}
  \grant{AIxCC: Automating real-world vulnerability discovery and remediation}{NYU}{99.9M}{PI}{24.09 -- 26.02}
  \grant{Research on building an open source kernel security model}{NSRI}{54.5M}{PI}{24.04 -- 24.10}
  \grant{Revisiting IoT threat models for smart cities and developing a vulnerability analysis system based on these models}{IITP}{400M}{PI}{24.01 -- 25.12}
  \grant{Building a system to assist variant analysis for browsers}{NRF}{65M}{PI}{23.06 -- 24.05}
  \grant{Generating a security model based on JavaScript intermediate language}{NSRI}{54.5M}{PI}{23.04 -- 23.10}
  \grant{Verifying security threats in open-source operating systems}{NSRI}{54.5M}{PI}{23.04 -- 23.10}
  \grant{Browser fuzzing with formal verification for cross architectures}{NRF}{110M}{PI}{22.09 -- 23.09}
  \grant{Building test suites for validating vulnerability detection}{ETRI}{27.3M}{PI}{22.08 -- 22.11}
  \grant{Generating a security model based on JavaScript security analysis}{NSRI}{54.5M}{PI}{22.04 -- 22.10}
  \grant{Developing techniques for collection and integrated analysis of automotive systems through event-based experimental systems}{Dankook university}{300M $\times$ 0.5}{Co-PI with Prof. Yujip Won}{22.04 -- 23.12}
  \grant{6G security}{Samsung Electronics}{200M $\times$ 0.2}{Co-PI with Prof. Yongdae Kim}{21.08 -- 23.09}
  \grant{DRAM security}{Samsung Electronics}{180M $\times$ 0.2}{Co-PI with Prof. Yongdae Kim}{21.07 -- 24.06}
  \grant{Systematic and precise transformation of the Qualcomm Hexagon architecture into intermediate representations for binary analysis}{NRF}{46.7M}{PI}{21.06 -- 22.05}
  \grant{Automatically generating a security model for discovering web browser vulnerabilities}{NSRI}{54.5M}{PI}{21.04 -- 21.10}
  \grant{Developing a scalable cyber reasoning system (Start-up)}{KAIST}{150M}{PI}{21.02 -- 24.12}
\end{etaremune}

\sectiontitle{Advising and Mentoring}
  \textbf{Ph.D. Students}
  \begin{itemize}[label=--,leftmargin=1.5em]
    \small
      \item Donghyeon Kim
      \item Dongjun Lee
      \item Eunkyu Lee
      \item Haein Lee
      \item Junyoung Park
      \item Minwoo Baek
      \item Sujin Han
  \end{itemize}

  \textbf{Master Students}
  \begin{itemize}[label=--,leftmargin=1.5em]
    \small
      \item Gunhee Ahn
      \item Juhyun Song
      \item Kyeongmin Kim
      \item Minwoo Jeong
  \end{itemize}

  \textbf{Alumni (Ph.D.)}
  \begin{itemize}[label=--,leftmargin=1.5em]
    \small
      \item HyungSeok Han (Co-advising with Yongdae Kim), Postdoc at Georgia Tech \hfill Ph.D. in 2023
  \end{itemize}

  \textbf{Alumni (M.S.)}
  \begin{itemize}[label=--,leftmargin=1.5em]
    \small
      \item Dong-uk Kim, 78ResearchLab \hfill M.S. in 2025
      \item Dongok Kim, ENKI WhiteHat \hfill M.S. in 2025
      \item Hyeon Heo, ENKI WhiteHat \hfill M.S. in 2025
      \item Seunggi Min, Financial Security Institute \hfill M.S. in 2025
      \item Wonyoung Kim, Samsung \hfill M.S. in 2025
      \item Taisic Yun, Theori \hfill M.S. in 2024
      \item Wonyoung Jung, 78ResearchLab \hfill M.S. in 2024
      \item Hyunsik Jeong (Co-advising with Yongdae Kim), S2W \hfill M.S. in 2021
  \end{itemize}

\end{document}
